---
title: "Lab 1 - Data visualization"
author: "Grace Romero"
format: pdf
editor: visual
editor_options: 
  chunk_output_type: console
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```

## Exercise 1

```{r ex-1, message=FALSE, warning=False}
#population_density_histogram

ggplot(data = midwest,
       aes(x=popdensity)) + 
    geom_histogram(binwidth = 10000, fill = "blue") + labs(title= "Population Density vs. Counties in the Midwest",x= "Population Density",y="Midwest Counties")
```

The shape of this is histogram is skewed right. Additionally, there do seem to be outliers because on the tail of the plot, there is a small blue bar indicating that there are data points between x = 75000 and x = 10000.

## Exercise 2

```{r ex-1, message=FALSE, warning=False}

#college_degree_vs_poverty_scatterplot

ggplot(data = midwest,
       aes(x=percollege, y = percbelowpoverty, color = state)) + 
    geom_point() + labs (title= "Percentage of People with College Degree vs. Percentage Below Poverty",x= "% with College Degree", y="% Below Poverty",legend = "State") + scale_colour_viridis_d()
```

## Exercise 3

In the data plot from Exercise 2, I observe that as the percentage of people with a college degree increases, the percentage of people below poverty decreases. It seems that in all of the states, these variables are associated. I don't think this relationship is linear because there is a lot of curvature in the trend of the data. It seems that the data from all of the states have similar tendencies, but there are a few distributional differences. For example, the points representative of people in Wisconsin begin higher on the y-axis than the points representative of people in the other three states.

## Exercise 4

```{r ex-1, message=FALSE, warning=False}

#college_degree_vs_poverty_smooth_curve_fit

ggplot(data = midwest,
       aes(x=percollege, y = percbelowpoverty, color = state, se = FALSE)) + 
    geom_smooth() + labs (title= "Percentage of People with College Degree vs. Percentage Below Poverty",x= "% with College Degree", y="% Below Poverty",legend = "State") + scale_colour_viridis_d()
```

I prefer this plot to the plot from Exercise 3. This is because I can more clearly see the general tendencies of the data in this plot than in the other one. I can also more clearly identify the differences between the states with this plot because it is easier to compare four lines than a large number of dots.

## Exercise 5

## Exercise 6

## Exercise 7
