---
title: "Lab 1 - Data visualization"
author: "Grace Romero"
format: pdf
editor: visual
editor_options: 
  chunk_output_type: console
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```

## Exercise 1

```{r ex-1, message=FALSE, warning=False}
#population_density_histogram

ggplot(data = midwest,
       aes(x=popdensity)) + 
    geom_histogram(binwidth = 10000, fill = "blue") + labs(title= "Population Density vs. Counties in the Midwest",x= "Population Density",y="Midwest Counties")
```

The shape of this is histogram is skewed right. Additionally, there do seem to be outliers because on the tail of the plot, there is a small blue bar indicating that there are data points between x = 75000 and x = 10000.

## Exercise 2

```{r}

#college_degree_vs_poverty_scatterplot

ggplot(data = midwest,
       aes(x=percollege, y = percbelowpoverty, color = state)) + 
    geom_point() + labs
(title= "Percentage of People with College Degree vs. Percentage Below Poverty",
  x= "% with College Degree",
  y="% Below Poverty", 
  legend = "State") + scale_colour_viridis_d()
```

## Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

## Exercise 4

## Exercise 5

## Exercise 6

## Exercise 7
